\section{Comparison of Data Mixtures}

Current works, including Common Pile, Phi-4, Nemotronc-CC, has combined web, web-rewrite, synthetic-instruction data, code data and curated in various proportions. We note that Comma0.1, upsampled peSo 16x for example, and that dataset makes 27\% of the training dataset, which is believed to improve the evaluation performance of the dataset. Comma0.1 also includes a very small set of instruction data from their DPI subset. Similarly, Phi4 performed ablations to find an optimal mixture of synthetic to organic data, but do not release their datasets. 

Unlike Comma0.1, we limited the amount of peSo in order to test the perofmance of our organic-synthetic mixture, Like Phi-4, our work also shows that a large proportion of synthetic/instruct data is also helpful in boosting performance, albeit at lower token counts, then either of these dataset.

We present below a comparison of data mixture. As shown, we did not repeat any portion of our dataset. As a contribution for future researchers, we believe using our dataset in addition to other permissive datasets such as Comma0.1, and repeating different portions, such as the synthetic instruct portion.

\begin{table}[h!]
\centering
\caption{Data Mixture Comparison: Phi-4 \citep{abdin2024phi4technicalreport} vs. Our Project}
\label{tab:my_table}
\begin{tabular}{lcccccc}
\toprule
\textbf{Data Source} & \multicolumn{3}{c}{\textbf{Fraction of Training (with Repeats)}} & \multicolumn{3}{c}{\textbf{Unique Token Count}} \\
\cmidrule(lr){2-4} \cmidrule(lr){5-7}
 & \textbf{Phi-4} & \textbf{Common Pile} & \textbf{\MixtureVitae{}} & \textbf{Phi-4} & \textbf{Common Pile} & \textbf{\MixtureVitae{}} \\
\midrule
Web & 15\% (1.2) & 8.7\% (6.0) & 4.4\% (1) & 1.3T & 14.52B & 9.314B \\
Web rewrites & 15\% (5.2) & -- & 3.7\% (1) & 290B & -- & 7.924B \\
Synthetic & 40\% (13.8) & 0.5\% (6.0) & 42.3\% (1) & 290B & 0.85B & 89.441B \\
Code data & 20\% (2.4) & 33.3\% (4.5) & 8.8\% (1) & 820B & 98.85B & 18.640B \\
Curated & 10\% (1.7) & 57.4\% (3.4) & 41.3\% (1) & 580B & 406.49B & 87.324B \\
\midrule
\textbf{Total} & \textbf{100\%} & \textbf{100\%} & \textbf{100\%} & \textbf{3.28T} & \textbf{520.71B} & \textbf{211.341B} \\
\bottomrule
\end{tabular}
\end{table}
