\section{Synthetic Data}
\begin{itemize}
\item 

\textbf
[HHN: None of this is included. We need to list the current datasets]
{Multiple-Choice Question (MCQ) Generation}: We generate multiple-choice questions (MCQs) derived from rich knowledge sources such as GenericsKB\cmt[VM]{What were the other knowledge sources? Let's be exhaustive.}, as well as abstract infill templates from the OIG dataset. These MCQs are intended to promote the ability to answer multiple choice questions. \cmt[VM]{Need more details. which model and which seed data?}

\item \textbf{Synthetic Stories}: We generated synthetic stories similar to TinyStories, based on datasets like Atomic 2024, and select portions of the PG-19 dataset. \cmt[VM]{Need more details. which model and which seed data?}

\item \textbf{Mathematical Generation}:
  \begin{itemize}
  \item We create math textbooks for specific complex topics by combining mathematical instruction seed data with open-source mathematical web texts. The goal of this dataset is to teach the model about basic math such as arithmetic and algebra. \cmt[VM]{Need more details. which model and which seed data?}
  \item We also create synthetic math questions and answers to teach basic math as well. \cmt[VM]{same as above}
  \end{itemize}

\item \textbf{Instruction Generation}: The instruction generation pipeline creates structured instructions, stories, and data analysis summaries, similar to Ultra-Magpie from SmolLM, but without editing instructions.
\end{itemize}

% Multiple-Choice Question (MCQ) Generation: We generate multiple-choice questions (MCQs) derived from rich knowledge sources such as\cmt[VM]{Need to be precise} GenericsKB\cmt[VM]{What were the other knowledge sources? Let's be exhaustive.}, as well as abstract infill templates from the OIG dataset. These MCQs are intended to promote the ability to answer multiple choice questions\cmt[VM]{need citation}.
% Synthetic Stories: We generated synthetic stories similar to TinyStories, based on datasets like Atomic 2024, and select portions of the PG-19 datasetquestions\cmt[VM]{what purpose does it serve? relevant cites?}.
% Mathematical Generation:
% We create math textbooks for specific complex topics by combining mathematical instruction seed data with open-source mathematical web texts. The goal of this dataset is to teach the model about basic math such as arithmetic and algebra\cmt[VM]{need more details}.
% We also create synthetic math questions and answers to teach basic math as well\cmt[VM]{need more details}.
% Instruction Generation: The instruction generation pipeline creates structured instructions, stories, and data analysis summaries, similar to Ultra-Magpie from SmolLM, but without editing instructions\cmt[VM]{need more details}.