
We present \MixtureVitae{}, an open‑access\footnote{Dataset, source code for experiments reproduction and pre-trained models will be revealed upon acceptance.} pretraining corpus built to minimize legal risk while providing strong downstream performance.  \MixtureVitae{} follows a permissive‑first, risk‑mitigated sourcing strategy that combines public‑domain and permissively licensed text (e.g., CC‑BY/Apache) with carefully justified low‑risk additions (e.g., government works and EU TDM‑eligible sources). \MixtureVitae{} adopts a simple, single-stage pretraining recipe that integrates a large proportion of permissive synthetic instruction and reasoning data—signals typically introduced during post-training and generally scarce in permissive web corpora. We categorize all sources into a three-tier scheme that reflects varying risk levels and provide shard-level provenance metadata to enable risk-aware usage. In controlled experiments using the open‑sci‑ref training protocol (fixed architectures and hyperparameters; 50B and 300B token budgets across 130M–1.7B parameters), models trained on \MixtureVitae{} consistently outperform other permissive datasets across a suite of standard benchmarks, and at the 1.7B-parameters/300B-tokens setting, they surpass FineWeb‑Edu and approach DCLM late in training. Performance is particularly strong on MMLU and on math and code benchmarks: a 1.7B model pretrained on 300B \MixtureVitae{} tokens matches or exceeds a strong 1.7B instruction‑tuned baseline on GSM8K, HumanEval, and MBPP, despite using over 36$\times$ fewer tokens (300B vs.\ $\approx$11T). Supported by a thorough decontamination analysis, these results show that permissive‑first data with high instruction and reasoning density, tiered by licensing and provenance-related risk, can provide a practical and risk-mitigated foundation for training capable LLMs, reducing reliance on broad web scrapes without sacrificing competitiveness.


% We present \MixtureVitae{}, a carefully curated collection of diverse, high-quality, permissive text data designed to support the training of large language models without copyright concerns. Comprising approximately \textbf{\DatasetSize{}} billion text tokens sourced from public domain, out-of-copyright, or permissively licensed materials, \MixtureVitae{} challenges the common notion that high-performance models require copyrighted content. We demonstrate that permissive-only data can yield strong models. Our dataset combines web-based open datasets, curated collections, and synthetic generations, all filtered and processed to ensure quality, diversity, and ethical use. \MixtureVitae{} is designed to lessen risk of copyright issues for model trainers while preserving model quality. We validate the dataset quality by training a reference baseline on various model and token scales and demonstrating superior performance to other open permissive datasets.

%\cmt[VM]{Can we be more specific? Does this mean mitigating the risk of statutory damages, or avoiding direct infringement claims?} [HHN: it lowers the risk to the data trainer but not necesarily to the end user.]%We validate the dataset quality by training a reference baseline - open-sci-ref - on various model and token scales, which allows us to compare to other open permissive datasets CommonCorpus and Comma-0.1 (derived from CommonPile).