\section{Discussion \& Conclusion}

% We have presented \MixtureVitae{}, a large pretraining corpus serving as a proof-of-concept: permissively licensed and permissively-sourced synthetic data can achieve high performance. Our experiments confirm that models trained on \MixtureVitae{} not only outperform other permissive datasets but also narrow the performance gap with leading models trained on proprietary or non-permissive data. On math and code tasks, a \MixtureVitae{}-trained base model matches or outperforms even base models like SmolLM2, despite their use of significantly larger compute and sophisticated multistage pretraining on non-permissive data. This outcome, together with the performed ablations, validates our data curation strategy and is consistent with the findings of \cite{abdin2024phi4technicalreport}. It demonstrates that the inclusion of a large fraction of reasoning, math, and instruction data---both real and synthetic---in the pretraining can already instill skills that are clearly absent when training on standard web-scrape corpora. Our work thus provides a path towards creating scalable datasets based on permissive sources, without having to sacrifice performance as compared with non-permissive ones.

We have introduced \MixtureVitae{}, a pretraining corpus serving as a proof-of-concept: \textbf{Permissively licensed and permissively-sourced} real and synthetic data can achieve high performance. Our results suggest a shift in the \textbf{compliance--performance frontier}. \MixtureVitae{} demonstrates that  capabilities previously associated with mixed-license corpora are reachable with a permissive first, risk-mitigated approach. In our controlled 300B-token experiments, not only does \MixtureVitae{} catch up to leading non-permissive baselines like DCLM and FineWeb-Edu, but our 1.7B base model also outperforms the \textit{post-trained} SmolLM2-1.7B-Instruct---a model trained on $\approx$11T tokens---on GSM8K, HumanEval and MBPP. 

\textbf{Dominant fraction of reasoning \& instruction data in the pre-training.} \MixtureVitae{}’s performance is enhanced by the large proportion of reasoning and instruction data, as demonstrated in the ablation study in Section~\ref{app:ablations}. Removing this subset (“w/o Instructions” in Figure~\ref{fig:ablate_all}) causes a substantial degradation across tasks—far larger than the impact of removing the web component. This observation validates and extends the findings of Phi-4~\citep{abdin2024phi4technicalreport}. Importantly, we show that heavily increasing reasoning and instruction data fraction on expense of generic web text creates overall boost in performance, specifically on math/code tasks (Tab. \ref{tab:instruct_results}), \textit{without} hurting core language understanding capabilities (Fig.~\ref{fig:300b_performance}, Tab. \ref{tab:lang_results}). 

% Via decontamination control experiments we also make sure that observed advantage is not due to test set leakage.

% \textbf{Mixing dominant fraction of reasoning \& instruction data into pre-training.} \MixtureVitae{}’s performance is enhanced by the large proportion of reasoning and instruction data, as demonstrated in the ablation study in Section~\ref{app:ablations}. Removing this subset (“w/o Instructions” in Fig.~\ref{fig:ablate_all}) causes a substantial degradation across tasks—far larger than the impact of removing the web component. This observation validates and extends the findings of Phi-4~\citep{abdin2024phi4technicalreport}, showing that a permissive-first, risk-mitigated, and reasoning-heavy mixture can substitute vast quantities of generic web text, particularly under constrained token budgets. Importantly, while strongly boosting the performance on math/code tasks (Tab. \ref{tab:instruct_results}), language understanding evals also stays strong, matching non-permissive baselines and outperforming other permissive datasets (Fig.~\ref{fig:300b_performance}, Tab. \ref{tab:lang_results}). We thus provide evidence that heavily increasing reasoning and instruction data fraction on expense of generic web text creates overall boost in performance without hurting core language understanding capabilities.
% showing that a permissive-first, risk-mitigated, and reasoning-heavy mixture can substitute vast quantities of generic web text, particularly under constrained token budgets.

% Building upon the work of Phi-4~\citep{abdin2024phi4technicalreport}, this confirms that a high-quality, permissive-first dataset---rich in reasoning and instruction data---can effectively substitute for vast quantities of broadly scraped web text.

%\subsection{Role of Instruction and Reasoning Data}
%\label{sec:role_of_instruction}
%\MixtureVitae{}’s performance is enhanced by the large proportion of reasoning and instruction data, as demonstrated in the ablation study in Section~\ref{app:ablations}. Removing this subset (“w/o Instructions” in Figure~\ref{fig:ablate_all}) causes a substantial degradation across tasks—far larger than the impact of removing the web component. This effect validates and extends the findings of Phi-4~\citep{abdin2024phi4technicalreport}, showing that a permissive-first, risk-mitigated, and reasoning-heavy mixture can substitute vast quantities of generic web text, particularly under constrained token budgets.

Beyond this specific corpus, the three‑tier licensing scheme and its shard‑level annotations
provide a \textbf{concrete template for structuring risk‑mitigated mixtures in future work}, and
\MixtureVitae{} as a whole serves as a reusable blueprint for compliant pretraining.
We demonstrate a pipeline built on positive‑inclusion “pseudo‑crawling,” tiered provenance
tracking, targeted synthetic generation with audited seeds and careful decontamination against test set leakage. As detailed in our scaling outlook (Appendix~\ref{app:scaling_outlook}), this recipe provides a path to extend compliant pretraining to the multi-trillion-token regime---via subset upsampling, multilingual expansion, and synthetic growth---providing the community with a sustainable alternative to the legal uncertainty of broad web scrapes.